\LARGE \bf Blockchain for routing correctness?

### 2018-07-19 paper.tex
added sections about bloom filters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. A given routing update for prefix X is \textit{correct} if for every AS in the final AS-path the AS-path that was used to create the AS’s respective routing update is still the most recent and valid for destination prefix X. Since BGPsec and RPKI do not provide correctness, this paper explores Blockchain-Merkle BGP (BM-BGP) which uses of blockchain and indexed merkle trees to provide correctness within the time frame of consensus in a chosen consensus protocol. The indexed merkle structure analyzed does not scale well because merkle roots on the blockchain cannot be updated and still have previous merkle verification work without at least log2(n) hashes (where n is leaf nodes in tree) sent to each node trying to validate the correctness of a transaction. This paper only explores theory and does not test the protocol. Sample code for IP indexed merkle trees: https://goo.gl/1DqDP3

@@

\section{Introduction}
External gateway protocols such as BGP suffer from data availability problems. This paper explores whether blockchain can be used alongside BGPsec to provide a proof of correctness for routing updates. Specifically, this paper explores whether IP indexed merkle trees can be used to create common knowledge of data correctness to the relevant parties whenever a routing update is received.

Proof of correctness has 3 parts: integrity, identity, and currentness. RPKI and BGPsec (when implemented) provide full integrity, full identity, and partial correctness. In BGPsec, there is a timestamp, however, it does not guarantee that a given routing update is the most recent one because updates can be withheld because of misconfigurations, new filters, or malicious ASes.

The explored blockchain is called Blockchain-Merkle BGP. Blockchain is used to create an ordering of routing tables and indexed merkle trees are used to conceal and ensure that routes are up-to-date. This paper shows that if merkle trees can adjust when some routing roots change, without resending the full merkle verification, then routing updates can be checked at any time efficiently against the ledger/blockchain for correctness.

@@

There are two shortcomings in this draft. First, the fact that BGP upgrades are so slow means that this protocol, even if fleshed out, would probably not ever be considered as an addition to BGP--the work is worthless if nearly worthless if only applicable to BGP. The goal in the future is see if similar ideas can be applied to the Bitcoin Lightning Network. Second, I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.

\subsection{Structure of Paper:
}

(1) BGP introduction: protocol, vulnerabilities, RPKI, and BGPsec

(2) Blockchain introduction: Byzantine generals problem, Nakamoto consensus, blockchain vulnerabilities, other consensus mechanisms (Ripple), merkle trees

(3) Correctness: causes of withholding and current solutions (IRR, looking glass)

(4) Blockchain for BGP Analysis: indexed merkle trees, variant of Ripple consensus, scalability

(5) Further Work: testing data availability problem in BGP and other networks (bitcoin lightning network)

@@

Border Gateway Protocol (BGP) is the external gateway routing protocol of the Internet [Butler, RFC1771, RFC4271]. Autonomous Systems (AS) are nodes that are controlled by ISP’s, transit providers, backbones, governments and other Internet actors use BGP to propagate routes to IP address destination prefixes. For each IP prefix (issued by ICANN or RIR) controlled by an AS, the AS will send a new route to each of its peers−−this originates the route. Each AS that receives updates for a specific destination prefix chooses one of the updates, often determined by the shortest number of hops (AS-path) to the destination. Then the AS adds its autonomous system number (ASN) to the route (sometimes multiple times) and forwards the route to its BGP peers. Each node in BGP has a different and incomplete view of the network. The diagram below shows a simple example of BGP.

@@

In order to limit the amount of “forks,” traditional blockchain solutions, such as in Bitcoin, make it costly to produce blocks−−this is called mining. The two general forms of mining that make valid block creation more costly in a decentralized fashion are Proof of work (POW) and proof of stake (POS). POW adds an extra limitation to what constitutes a valid block, that is, valid blocks have to hash to a value that is smaller than some predefined number. The predefined number changes periodically in order to keep block creation within some average window of time, limiting forks. In POW, the longest valid chain is the “correct” chain because it has the most work attached to it. POS is another mechanism where block producers are chosen based on some stake in the system, more specifically some amount of coin and often some attributes of the coin, such as how long the coin has been stored for. POW and POS are mechanisms for ordering transactions and they successfully stop double spending (note that POS research is still in the works with Casper, Ouroborus, etc).

@@

\subsection{Attacking the Blockchain}
Various attacks come out of POW and POS when too much of the nodes mining (“miners”) control block production, meaning that they have the resources to fork at any point in the chain and eventually create a longer valid chain. These attacks are all possible if miners get more than 50\% of the block production resources, which is why it is called the “51\% attack” (although more accurately named the “$>$50\% attack”) (Nakamoto p.6). The 51\% attack allows for censorship and double spending. Miners have an incentive to pool resources and share rewards because miners want more frequent payments. If miner’s pool into a large enough group ($>$50\% of resources) then the 51\% attack can be performed. Dr. Emin Sirer found that the 51\% attack can occur lower if miners perform “selfish mining.” Selfish mining is strategically withhold- ing blocks and mining on the hidden blocks, in order to maximize profit. With selfish mining, the 51\% attack can be performed by a mining pool/entity that has $>$25\% of the resources (Eyal 2013).

@@

\subsection{Definitions}
\textit{Correctness}: A given routing update for prefix X is \textit{correct} if for every AS in the final AS-path the AS-path that was used to create the AS’s respective routing update is still the most recent and valid for destination prefix X.

@@

The second type of incorrectness, withholding routing updates, is the type of incorrectness focused on in this paper. There are two reasons for withholding routing updates, although the list is probably not exhaustive. The first reason is from misconfigurations. A router may not have the appropriate input or output policy configured correctly for a specific IP prefix [Wang, p.1-22009; Feamster , cite Mahajan]. The second reason is malicious transit providers. The diagram below shows both scenarios.\footnote{Author's note: I have not been able to find malicious transit providers in the literature but it is theoretically possible.}

@@

@@

There is a stronger view of correctness would also be beneficial if it could be reached as it would by definition prevent unexpected traffic flow scenarios. If there was a way to knowledge about selective of route advertisements, unexpected traffic flows could be more easily avoided [cite rfc 7789] and strong correctness achieved.

@@

Network operators have a limited view of the BGP network which is by design to reduce unnecessary routing updates to prefixes that are not obtainable and reduce the complexity of path selection and local policy management. Looking Glass servers and Internet Routing Registries have been used to give network operators difference perspectives of the network that they could see from an AS they controlled. LG and IRR help with detecting misconfigurations [cite Bruno].

@@

Definitions 
Routing root: the root of the indexed merkle tree of routing updates

Correctness of routing updates can be achieved with consensus of routing tables. BM-BGP provides consensus of routing tables in a way that preserves privacy and is more scalable than creating a global consensus of routing tables. Each AS sends a merkle verification alongside a routing update that builds the most recent root in the blockchain for that AS. Like BGPsec signatures, the merkle hash lists for each AS are passed on in each new downstream update so that every AS has all the previous hash lists to rebuild all of the merkle trees for all the ASes in the AS-path. Although merkle trees reduce on-chain data substantially, they are not scalable enough to make BM-BGP feasible because old merkle proofs have to be retained in every routing root update (see Consensus Protocol section). Fig. 4. shows the blockchain with merkle roots.

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.40]{Blockchain1.png}
    \end{figure}

In this setup, routes can be checked as correct by an AS by running an isCorrect() function that iterates through each route, grabs the routing root for the AS in the blockchain in the most recent block (unless local time is not yet greater than the commitRoutingRootAtTime parameter that is in the update), and use the hashes to build the merkle root. If the root does not match the hash path, there is a grace period where the route is used even though correctness is not proven until there has been a substantial wait since commitRoutingRootAtTime to make the AS very confident that the routing root commit would have been part of the blockchain by now if it had been in fact submitted on time.

\subsection{Integration with BGPsec}
MBGP integrates well with BGPsec because the path that is added to the blockchain does not include AS prepending. The path that is put on the blockchain is only the path created from each secure-path segment of a BGPsec update ,not including prepending count (pCount).

\section{Indexed Merkle Tree}
Each AS has the ability track two routing roots on the blockchain, one sequence of routing roots for IPv4 and the other sequence for IPv6. In order for merkle trees to be effective for providing correctness to routing updates they most have the following property.

\textit{Correctness requirement}: the hashes that verify that a route to prefix X is in the tree must also show that the route is in a subtree of all other routes to the same prefix and the subtree is in the correct position in the main tree.

@@

The tree follows the integrity property because the tree is indexed by IP addresses. Left branches are an additional zero from the parent node and right branches are an additional one from the parent node. For example, the position of a route to IP prefix 160.0.0.0/3 would be right branch (for first bit), left branch (for second bit), right branch (for third bit). If there are routes to destinations that are of a greater prefix, say 160.0.0.0/17, then 160.0.0.0/3 becomes a middle node. There are three possible children from a parent: left, middle, right. Middle is used when there are routes underneath the position of the route in the tree. Middle nodes are needed in order to keep the integrity of the tree so that the integrity property is followed. There is no other way to guarantee that there is not more than one route to 160.0.0.0/3 in a tree that also has 160.0.0.0/17 without adding a middle node for 160.0.0.0/3. Therefore, the routing tree differs from a normal merkle tree not only in that the routing tree is indexed but also because the routing tree needs to allow for leaf nodes below any parent of the tree. A. Tree creation algorithm The algorithm for forming the most efficient tree is three steps: create an inefficient tree, condense the tree, recursively hash nodes to form root. To create an inefficient tree, first you take the list of routes in the routing table and add them to the tree. Routes are put into an array and recursively added to the tree based on the binary prefix of each route. The recursive function searches through each route in the array and calls the function again with a new list of routes that have a specific bit sequence in the prefix. This process continues, the bit sequence gets longer and more and more routes get filtered out. A route is added to the tree when the bit sequence matches the route prefix exactly. If a node is added tree but there are still nodes left that get added under it, that node turns into a middle node.

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.40]{inefficient.png}
    \caption{This tree can be condensed by moving Route 32.0.0.0/3 up to be a left sibling of h2. Routes 128.0.0.0/2 and 192.0.0.0/2 can be moved up with instructions to skip the 2nd after if the first bit is a 1.}
    \end{figure}

@@

The core problem behind route omission is that ASes end up with inaccurate updates for a destination, which may lead to suboptimal ”best path” decisions. If all ASes commit publically to a specific table, then route omission cannot happen because there is only one possible path that is timestamped for every subset of the path. However, committing publically to a routing table is not scalable or desired by ASes. The amount of data of every update of every AS is substantial, and it is obvious that a consensus protocol could not handle this much data. Committing every update is also not desirable because many ASes do not want anyone to be able to see their routing table. As addressed in the previous section, indexed merkle trees are used for compact integrity which hide routing information from non-peers of an AS.

@@

Blockchain without 2nd layer is not scalable because consensus--the process of minimizing the probability of forks and maximizing the probability of state change immutability--is achieved by setting a sufficiently high block creation interval through mining and a cap on valid block size. Traditional blockchains need to achieve agreement/consensus with the free entry and exit of nodes, and there is no hierarchy or identity of nodes where nodes may have special permissions--this is part of what we mean by ”decentralization.” Since the cost of creating a node is so low in traditional blockchains, it is very hard to achieve consensus, and a mining mechanism must exploit a scarce resource in order to bring scarcity to valid block producers.

@@

\subsection{Multi-block Merkle Verification}

A critical problem with the indexed Merkle tree construction is that hashes have to build up to the merkle tree for every route when new routing roots are committed. One way to do this is to attach hashes of all of the leaf nodes in the tree to every update--however this defeats one of the main purposes of using a merkle tree in the first place. This critical problem is one that I have not solved yet and may be fatal to the project.

@@

Instead of a consensus algorithm ordering routing routes, ICANN and RIRs can order routing routes because they are trusted entities. It is unlikely that these organizations would take on this role, but in a hypothetical world where they ordered routing roots, route omission and selective lying could be solved in the same way a consensus protocol solves route omission and selective lying. Centralizing ordering of routing roots has a scaling advantage because a centralized algorithm can order transactions much more quickly than any consensus protocol. The algorithm that the centralized entity runs could be as simple as choose the first valid and received routing root, which would solve any data conflicts where there are more than one new routing root for an AS.

@@

2. Test BH-BGP alongside a simulation BGP network.

3. Compare effectiveness of Looking Glass with BH-BGP

@@

5. Apply BH-BGP to Bitcoin Lightning Network protocols

@@

\bibitem{c1}Back, A., et. al. (2014). Enabling blockchain innovations with pegged sidechains. https://blockstream.com/sidechains.pdf
\bibitem{c2} BIP 148. github.com/bitcoin/bips/blob/master/bip-0148.mediawiki
\bibitem{c3} Bruno., L., et. al. (2014) Through the Looking-Glass, and What Eve Found There. http://s3.eurecom.fr/docs/woot14\_bruno.pdf
\bibitem{c4} Buterin. V (2017). Hard forks, soft forks, defaults and coercion https://vitalik.ca/general/2017/03/14/forks\_and\_markets.html
\bibitem{c5} Buterin., V. (2017) Minimum viable plasma. ethresear.ch/t/minimal-viable-plasma/426
\bibitem{c6} Buterin, V., Poon, Joseph. (2017). Plasma: Scalable Autonomous Smart Contracts https://plasma.io/plasma.pdf
\bibitem{c7} Butler, K., Farley, T., McDaniel, P., \& Rexford, J. (2008). A
Survey of BGP Security Issues and Solutions. 1-37. https://www.cs.princeton.edu/~jrex/papers/bgp-security08.pdf
\bibitem{c8} Eyal, I., \& Sirer, E. G. (2013). Majority is not enough. Retrieved from http://arxiv.org/abs/1311.0243
\bibitem{c9}Feamster, N., Balakrishnan, H. (2005) Detecting BGP Configuration Faults with Static Analysis. https://www.usenix.org/legacy/event/nsdi05/tech/feamster/feamster.pdf
\bibitem{c10} Hari, A., \& Lakshman, T. V. (2016). The Internet Blockchain. Proceedings of the 15th ACM Workshop on Hot Topics in Networks - HotNets 16. Retrieved from http://web.kaust.edu.sa/Faculty/MarcoCanini/classes/CS390G/S17/papers/
InternetBlockchain.pdf
\bibitem{c11} Heilman E., Kendler A., Zohar A., and Goldberg S. (2015). Eclipse attacks on bitcoin’s peer-to-peer network. In USENIX Security Symposium. 129–144
\bibitem{c12} Poon, J., Dryja, T. (2015) The bitcoin lightning network: Scalable off-chain instant payments draft 0.5.9.1. https://lightning.network/lightning-network-paper.pdf
[12] Lamport, L.; Shostak, R.; Pease, M. (1982). "The Byzantine Generals Problem" (PDF). ACM Transactions on Programming Languages and Systems.
\bibitem{c13} Mahajan, R., et. al. (2002) Understanding BGP Misconfiguration. https://www.microsoft.com/en-us/research/wp-content/uploads/2017/01/Understanding-BGP-Misconfiguration.pdf
\bibitem{c14} Merkle, R. (1980). Protocols for public key cryptosystems. Symposium on Security and Privacy. IEEE Computer Society. 122-133.
\bibitem{c15} Massias, H., Avila, X., Quisquater, J., (1999). "Design of a secure timestamping service with minimal trust requirements," In 20th Symposium on Information Theory in the Benelux.

\bibitem{c16} Nakamoto, S. (2008). Bitcoin: A Peer-to-Peer Electronic Cash System.
1-9. Retrieved from https://bitcoin.org/bitcoin.pdf
\bibitem{c17} NIST. RPKI Deployment Monitor. (2018). Retrieved from https://rpki-monitor.antd.nist.gov/
\bibitem{c18} Rekhter, Y., Li, T. (1995) RFC 1771 A border gateway protocol 4 (BGP-4).
\bibitem{c19} Rekhter, Y., Li, T.  Hares, S. (2006) RFC4271 A Border Gateway Protocol 4 (BGP-4).
\bibitem{c20} RFC7789 Impact of BGP Filtering on Inter-Domain Routing Policies
\bibitem{c21} RFC8205 BGPsec Protocol Specification. M. Lepinski, Ed., K. Sriram, Ed..
     September 2017. (Format: TXT=115900 bytes) (Updated by RFC8206)
     (Status: PROPOSED STANDARD) (DOI: 10.17487/RFC8
\bibitem{c22} RFC8210 The Resource Public Key Infrastructure (RPKI) to Router Protocol,
     Version 1. R. Bush, R. Austein. September 2017. (Format: TXT=78467
     bytes) (Updates RFC6810) (Status: PROPOSED STANDARD) (DOI:
     10.17487/RFC8210)
\bibitem{c23} Schwartz, D., Youngs, N., \& Britto, A. (2014). The
Ripple Protocol Consensus Algorithm. 1-8. Retrieved from
https://ripple.com/files/ripple consensus whitepaper.pdf
\bibitem{c24} Shor. P. (1994) Algorithms for quantum computation: Discrete logarithms and factoring
\bibitem{c25} Toonk, A. (2017, December 12). Popular Destinations rerouted to Russia. Retrieved from https://bgpmon.net/popular-destinations-rerouted-to-russia/
\bibitem{c26} UASF Working Group. (2017). https://www.uasf.co/
\bibitem{c27} Wang, Y., et. al. (2009). Neighbor-Specific BGP: More Flexible Routing Policies While Improving Global Stability. https://arxiv.org/pdf/0906.3846.pdf
\bibitem{c28} Youtube Hijacking: A RIPE NCC RIS case study. (March 2008). ripe.net/internet-coordination/news/industry-developments/youtube-hijacking-a-ripe-ncc-ris-case-study.
\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. We define a given routing update for prefix X as \textit{correct} if for every AS in the AS-path of the update, the AS-path is still the most recent and valid for destination prefix X. This paper explores Blockchain-Merkle BGP (BM-BGP) which uses blockchain, indexed merkle trees, and bloom filters to provide correctness within the time frame of consensus in a chosen consensus protocol.

@@

\section{Introduction}
External gateway protocols such as BGP suffer from data availability problems. This paper explores whether blockchain can be used alongside BGPsec to provide a proof of correctness for routing updates. Specifically, this paper explores whether IP indexed merkle trees, blooms filters, and blockchain can be used to create common knowledge of route correctness to the relevant parties whenever a routing update is received.

Proof of correctness has 3 requirements: integrity, identity, and currentness. RPKI and BGPsec (when implemented) provide full integrity, full identity, and partial currentness. In BGPsec, there is a timestamp, however, it does not guarantee that a given routing update is the most recent one because updates can be withheld because of misconfigurations, new filters, or malicious ASes.

This paper proposes an algorithmic way to detect withholding of routes without using looking glass servers. Blockchain is used to create an ordering of routing tables and indexed merkle trees and bloom filters are used to ensure that routes are up-to-date in a scalable way.

@@

There are two shortcomings in this draft. First, the fact that BGP upgrades are so slow means that this protocol, even if fleshed out, would probably not ever be considered as an addition to BGP---the work is worthless or nearly worthless if only applicable to BGP. The goal in the future is see if similar ideas can be applied to the Bitcoin Lightning Network. Second, I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.

@@

Border Gateway Protocol (BGP) is the external gateway routing protocol of the Internet (Butler, RFC1771, RFC4271). Autonomous Systems (AS) are nodes that are controlled by ISP’s, transit providers, backbones, governments and other Internet actors use BGP to propagate routes to IP address destination prefixes. For each IP prefix (issued by ICANN or RIR) controlled by an AS, the AS will send a new route to each of its peers---this originates the route. Each AS that receives updates for a specific destination prefix chooses one of the updates, often determined by the shortest number of hops (AS-path) to the destination. Then the AS adds its autonomous system number (ASN) to the route (sometimes multiple times) and forwards the route to its BGP peers. Each node in BGP has a different and incomplete view of the network. The diagram below shows a simple example of BGP.

@@

In order to limit the amount of “forks,” traditional blockchain solutions, such as in Bitcoin, make it costly to produce blocks−-−this is called mining. The two general forms of mining that make valid block creation more costly in a decentralized fashion are Proof of work (POW) and proof of stake (POS). POW adds an extra limitation to what constitutes a valid block, that is, valid blocks have to hash to a value that is smaller than some predefined number. The predefined number changes periodically in order to keep block creation within some average window of time, limiting forks. In POW, the longest valid chain is the “correct” chain because it has the most work attached to it. POS is another mechanism where block producers are chosen based on some stake in the system, more specifically some amount of coin and often some attributes of the coin, such as how long the coin has been stored for. POW and POS are mechanisms for ordering transactions and they successfully stop double spending (note that POS research is still in the works with Casper, Ouroborus, etc).

@@

\subsection{Attacking the Blockchain}
Various attacks come out of POW and POS when too much of the nodes mining (“miners”) control block production, meaning that they have the resources to fork at any point in the chain and eventually create a longer valid chain. These attacks are all possible if miners get more than 50\% of the block production resources, which is why it is called the “51\% attack” (although more accurately named the “$>$50\% attack”) (Nakamoto p.6). The 51\% attack allows for censorship and double spending. Miners have an incentive to pool resources and share rewards because miners want more frequent payments. If miner’s pool into a large enough group ($>$50\% of resources) then the 51\% attack can be performed. Dr. Emin Sirer found that the 51\% attack can occur lower if miners perform “selfish mining.” Selfish mining is strategically withholning blocks and mining on the hidden blocks, in order to maximize profit. With selfish mining, the 51\% attack can be performed by a mining pool/entity that has $>$25\% of the resources (Eyal 2013).

@@

\subsection{Definitions}
\textit{Correctness}: A given routing update for prefix X is \textit{correct} if for every AS in the AS-path of the update, the AS-path is still the most recent and valid for destination prefix X.

@@

The second type of incorrectness, withholding routing updates, is the type of incorrectness focused on in this paper. There are two reasons for withholding routing updates, although the list is probably not exhaustive. The first reason is from misconfigurations. A router may not have the appropriate input or output policy configured correctly for a specific IP prefix (Wang p.1-2 2009, Feamster 2005, Mahajan 2002). The second reason is malicious transit providers. The diagram below shows both scenarios.\footnote{Author's note: I have not been able to find malicious transit providers in the literature but it is theoretically possible.}

@@

Strong correctness would also be beneficial if it could be reached as it would by definition prevent unexpected traffic flow scenarios. If there was a way to know about selective of route advertisements, unexpected traffic flows could be more easily avoided (RFC 7789) and strong correctness achieved.

@@

@@

Network operators have a limited view of the BGP network which is by design to reduce unnecessary routing updates to prefixes that are not obtainable and reduce the complexity of path selection and local policy management. Looking Glass servers and Internet Routing Registries have been used to give network operators difference perspectives of the network that they could see from an AS they controlled. LG and IRR help with detecting misconfigurations (Bruno 2014).

@@

\subsection{Definitions}
Routing root: the root of the indexed merkle tree of routing updates

\subsection{BM-BGP Protocol}

Correctness of routing updates can be achieved with consensus of routing tables. BM-BGP provides consensus of routing tables in a way that preserves privacy and is more scalable than creating a global consensus of routing tables. BM-BGP uses indexed merkle trees and bloom filters the limit the amount of information stored on the blockchain.

In BM-BGP, when an AS makes a new update, they submit a new routing root and a bloom filter to the blockchain. In the update, the AS adds a merkle verification that builds up the most recent root in the blockchain for that AS. Like BGPsec signatures, the merkle hash lists for each AS are passed on in each new downstream update so that every AS has all the previous hash lists to rebuild all of the merkle trees for all the ASes in the AS-path.

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.35]{Blockchain_merkle_3_.png}
    \end{figure}

In this setup, routes can be checked as correct by an AS by running an isCorrect() function that iterates through each route, grabs the routing root for the AS in the blockchain in the most recent block that contains a bloom filter with the IP prefix (unless local time is not yet greater than the commitRoutingRootAtTime parameter that is in the update), and uses the hashes to build the routing root.

\subsection{Integration with BGPsec}
MBGP integrates well with BGPsec because the path that is added to the blockchain does not include AS prepending. The path that is put on the blockchain is only the path created from each secure-path segment of a BGPsec update, not including prepending count (pCount).

BM-BGP requires routing updates to have all AS-paths to the destination that an AS would have propagated as the "best path" to at least one node. Only one of these paths is the best path in the update, but all of them are needed for proof of correctness. If only a subset of the paths were sent in a routing update, an AS receiving the update would not know if there was a more recent update that it should be receiving. With all of the best paths, the AS can track who propagated the update at a specific time. This means that whenever a new "best path" is chosen for a destination prefix X for any nodes, all nodes connected to the AS expect to receive a new update that contains the new best path even if it is not the best path that they have to follow.

Each AS has the ability track two routing roots on the blockchain, one sequence of routing roots for IPv4 and the other sequence for IPv6.

\section{Bloom Filters}
A bloom filter is a data structures used for determining elements in a group. False negatives are impossible and false positives are probabilistic depending on the number of cells and elements in the bloom filter (Bloom 1970).

Bloom filters are used in BM-BGP to provide information on what destination IP addresses have a different AS path. An AS can choose any AS and see if at least one of the paths to any destination prefix has been updated in a specific block on the blockchain. The AS does this by seeing if the IP address is in the bloom filter.

\section{Indexed Merkle Trees}
Indexed merkle trees must be used in order to guarantee that there are no hidden routes in the merkle tree. If merkle trees were not indexed, the bloom filter could indicate that there was a route change to destination X, but it could not prove that a specific update was one of the most recent ones.

In order for merkle trees to be effective for providing correctness to routing updates they most have the following property.

\textit{Correctness requirement}: the hashes that verify that a route to prefix X is in the tree must also show that the route is in a subtree of all other routes to the same prefix to the same prefix and the subtree is in the correct IP-indexed position in the main tree.

@@

The tree follows the integrity property because the tree is indexed by IP addresses. Left branches are an additional zero from the parent node and right branches are an additional one from the parent node. For example, the position of a route to IP prefix 160.0.0.0/3 would be right branch (for first bit), left branch (for second bit), right branch (for third bit). If there are routes to destinations that are of a greater prefix, say 160.0.0.0/17, then 160.0.0.0/3 becomes a middle node. There are three possible children from a parent: left, middle, right. Middle is used when there are routes underneath the position of the route in the tree. Middle nodes are needed in order to keep the integrity of the tree so that the integrity property is followed. There is no other way to guarantee that there is not more than one route to 160.0.0.0/3 in a tree that also has 160.0.0.0/17 without adding a middle node for 160.0.0.0/3. Therefore, the routing tree differs from a normal merkle tree not only in that the routing tree is indexed but also because the routing tree needs to allow for leaf nodes below any parent of the tree.

\subsection{Tree creation algorithm}

The algorithm for forming the most efficient tree is three steps: create an inefficient tree, condense the tree, recursively hash nodes to form root. To create an inefficient tree, first take the list of routes in the routing table and add them to the tree. Routes are put into an array and recursively added to the tree based on the binary prefix of each route. The recursive function searches through each route in the array and calls the function again with a new list of routes that have a specific bit sequence in the prefix. This process continues, the bit sequence gets longer and more and more routes get filtered out. A route is added to the tree when the bit sequence matches the route prefix exactly. If a node is added tree but there are still nodes left that get added under it, that node turns into a middle node.

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.35]{inefficient.png}
    \caption{This tree can be condensed by moving Route 32.0.0.0/3 up to be a left sibling of h2. Routes 128.0.0.0/2 and 192.0.0.0/2 can be moved up with instructions to skip the 2nd after if the first bit is a 1. Note that this tree only has one route destination prefix in the tree. Realistically, it should be expected that many destination prefix have more than one route because of multihoming and load balancing.}
    \end{figure}

@@

The core problem behind route withholding (incorrect data) is that ASes end up with inaccurate updates for a destination, which may lead to suboptimal ”best path” decisions. If all ASes commit publically to a specific table, then data withholding is detectable. However, committing publically to a routing table is not scalable or desired by ASes. The amount of data of every update of every AS is substantial, and it is obvious that a consensus protocol could not handle this much data. Committing every update is also not desirable because many ASes do not want anyone to be able to see their routing table. As addressed in the previous sections, indexed merkle trees and bloom filters are used for compact integrity which hides routing information from non-peers of an AS.

@@

Blockchain without 2nd layer is not scalable because consensus---the process of minimizing the probability of forks and maximizing the probability of state change immutability---is achieved by setting a sufficiently high block creation interval through mining and a cap on valid block size. Traditional blockchains need to achieve agreement/consensus with the free entry and exit of nodes, and there is no hierarchy or identity of nodes where nodes may have special permissions---this is part of what we mean by ”decentralization.” Since the cost of creating a node is so low in traditional blockchains, it is very hard to achieve consensus, and a mining mechanism must exploit a scarce resource in order to bring scarcity to valid block producers.

@@

@@

Instead of a consensus algorithm ordering routing routes, ICANN and RIRs can order routing routes because they are trusted entities. It is unlikely that these organizations would take on this role, but in a hypothetical world where they ordered routing roots, route update withholding could be solved in the same way a consensus protocol solves route it. Centralizing ordering of routing roots has a scaling advantage because a centralized algorithm can order transactions much more quickly than any consensus protocol. The algorithm that the centralized entity runs could be as simple as choose the first valid and received routing root, which would solve any data conflicts where there are more than one new routing root for an AS.

@@

2. Test BM-BGP alongside a simulation BGP network.

3. Compare effectiveness of Looking Glass with BM-BGP

@@

5. Apply BM-BGP to Bitcoin Lightning Network protocols

@@

\bibitem{c1}Back, A., et. al. (2014). Enabling blockchain innovations with pegged sidechains. https://blockstream.com/sidechains.pdf
\bibitem{c2} BIP 148. github.com/bitcoin/bips/blob/master/bip-0148.mediawiki
\bibitem{c3} Bloom, Burton H. (1970), "Space/Time Trade-offs in Hash Coding with Allowable Errors", Communications of the ACM, 13 (7): 422–426, doi:10.1145/362686.362692
\bibitem{c5} Bruno., L., et. al. (2014) Through the Looking-Glass, and What Eve Found There. http://s3.eurecom.fr/docs/woot14\_bruno.pdf
\bibitem{c6} Buterin. V (2017). Hard forks, soft forks, defaults and coercion https://vitalik.ca/general/2017/03/14/forks\_and\_markets.html
\bibitem{c7} Buterin., V. (2017) Minimum viable plasma. ethresear.ch/t/minimal-viable-plasma/426
\bibitem{c8} Buterin, V., Poon, Joseph. (2017). Plasma: Scalable Autonomous Smart Contracts https://plasma.io/plasma.pdf
\bibitem{c9} Butler, K., Farley, T., McDaniel, P., \& Rexford, J. (2008). A
Survey of BGP Security Issues and Solutions. 1-37. https://www.cs.princeton.edu/~jrex/papers/bgp-security08.pdf
\bibitem{c10} Eyal, I., \& Sirer, E. G. (2013). Majority is not enough. Retrieved from http://arxiv.org/abs/1311.0243
\bibitem{c11}Feamster, N., Balakrishnan, H. (2005) Detecting BGP Configuration Faults with Static Analysis. https://www.usenix.org/legacy/event/nsdi05/tech/feamster/feamster.pdf
\bibitem{c12} Hari, A., \& Lakshman, T. V. (2016). The Internet Blockchain. Proceedings of the 15th ACM Workshop on Hot Topics in Networks - HotNets 16. Retrieved from http://web.kaust.edu.sa/Faculty/MarcoCanini/classes/CS390G/S17/papers/
InternetBlockchain.pdf
\bibitem{c13} Heilman E., Kendler A., Zohar A., and Goldberg S. (2015). Eclipse attacks on bitcoin’s peer-to-peer network. In USENIX Security Symposium. 129–144
\bibitem{c14} Poon, J., Dryja, T. (2015) The bitcoin lightning network: Scalable off-chain instant payments draft 0.5.9.1. https://lightning.network/lightning-network-paper.pdf
[12] Lamport, L.; Shostak, R.; Pease, M. (1982). "The Byzantine Generals Problem" (PDF). ACM Transactions on Programming Languages and Systems.
\bibitem{c15} Mahajan, R., et. al. (2002) Understanding BGP Misconfiguration. https://www.microsoft.com/en-us/research/wp-content/uploads/2017/01/Understanding-BGP-Misconfiguration.pdf
\bibitem{c16} Merkle, R. (1980). Protocols for public key cryptosystems. Symposium on Security and Privacy. IEEE Computer Society. 122-133.
\bibitem{c17} Massias, H., Avila, X., Quisquater, J., (1999). "Design of a secure timestamping service with minimal trust requirements," In 20th Symposium on Information Theory in the Benelux.

\bibitem{c18} Nakamoto, S. (2008). Bitcoin: A Peer-to-Peer Electronic Cash System.
1-9. Retrieved from https://bitcoin.org/bitcoin.pdf
\bibitem{c19} NIST. RPKI Deployment Monitor. (2018). Retrieved from https://rpki-monitor.antd.nist.gov/
\bibitem{c20} Rekhter, Y., Li, T. (1995) RFC 1771 A border gateway protocol 4 (BGP-4).
\bibitem{c21} Rekhter, Y., Li, T.  Hares, S. (2006) RFC4271 A Border Gateway Protocol 4 (BGP-4).
\bibitem{c22} RFC7789 Impact of BGP Filtering on Inter-Domain Routing Policies
\bibitem{c23} RFC8205 BGPsec Protocol Specification. M. Lepinski, Ed., K. Sriram, Ed..
     September 2017. (Format: TXT=115900 bytes) (Updated by RFC8206)
     (Status: PROPOSED STANDARD) (DOI: 10.17487/RFC8
\bibitem{c24} RFC8210 The Resource Public Key Infrastructure (RPKI) to Router Protocol,
     Version 1. R. Bush, R. Austein. September 2017. (Format: TXT=78467
     bytes) (Updates RFC6810) (Status: PROPOSED STANDARD) (DOI:
     10.17487/RFC8210)
\bibitem{c25} Schwartz, D., Youngs, N., \& Britto, A. (2014). The
Ripple Protocol Consensus Algorithm. 1-8. Retrieved from
https://ripple.com/files/ripple consensus whitepaper.pdf
\bibitem{c26} Shor. P. (1994) Algorithms for quantum computation: Discrete logarithms and factoring
\bibitem{c27} Toonk, A. (2017, December 12). Popular Destinations rerouted to Russia. Retrieved from https://bgpmon.net/popular-destinations-rerouted-to-russia/
\bibitem{c28} UASF Working Group. (2017). https://www.uasf.co/
\bibitem{c29} Wang, Y., et. al. (2009). Neighbor-Specific BGP: More Flexible Routing Policies While Improving Global Stability. https://arxiv.org/pdf/0906.3846.pdf
\bibitem{c30} Youtube Hijacking: A RIPE NCC RIS case study. (March 2008). ripe.net/internet-coordination/news/industry-developments/youtube-hijacking-a-ripe-ncc-ris-case-study.
\end{thebibliography}
